### 2018-12-29 Sections/costs_and_attributes_in_quantum_networks.tex
Photos update

The purity of a state that was initially pure quantifies how well quantum coherence was maintained during evolution, equivalently how well superpositions are maintained. The purity is defined as,
\begin{align}
\mathcal{P}(\hat\rho) = \mathrm{tr}(\hat\rho^2),
\end{align}
where,
\begin{align}
\frac{1}{\mathrm{dim}(\hat\rho)} \leq \mathcal{P}(\hat\rho) \leq 1.
\end{align}
We have \mbox{$\mathcal{P}(\hat\rho) = 1$} iff \mbox{$\hat\rho=\ket{\psi}\bra{\psi}$} is a pure state, and \mbox{$\mathcal{P}(\hat\rho)=1/\mathrm{dim}(\hat\rho)$} iff \mbox{$\hat\rho=\mathbb{\hat{I}}/\mathrm{dim}(\hat\rho)$} is the maximally mixed state.

>>>>

The purity of a state that was initially pure quantifies how well quantum coherence was maintained during evolution, equivalently how well superpositions are maintained. The purity is defined as,
\begin{align}
\mathcal{P}(\hat\rho) = \mathrm{tr}(\hat\rho^2),
\end{align}
where,
\begin{align}
\frac{1}{\mathrm{dim}(\hat\rho)} \leq \mathcal{P}(\hat\rho) \leq 1.
\end{align}
We have \mbox{$\mathcal{P}(\hat\rho) = 1$} iff \mbox{$\hat\rho=\ket{\psi}\bra{\psi}$} is a pure state, and \mbox{$\mathcal{P}(\hat\rho)=1/\mathrm{dim}(\hat\rho)$} iff \mbox{$\hat\rho=\hat\openone/\mathrm{dim}(\hat\rho)$} is the maximally mixed state.

### 2018-12-29 Sections/entanglement_the_ultimate_quantum_resource.tex
Photos update

It turns out that there is one particularly useful quantum resource, that finds applicability in many of these protocols -- \textit{distributed entanglement}, which comes in many flavours and varieties, some of which we discuss now.

>>>>

It turns out that there is one particularly useful quantum resource, that finds applicability in many of these protocols -- \textit{distributed entanglement}\index{Entanglement!Distributed}, which comes in many flavours and varieties, some of which we discuss now.

### 2018-12-29 Sections/intro_to_QM.tex
Photos update

Therefore, referring back to the qubit example in Eq.~(\ref{eq:2x2density}), $a$ and \mbox{$1-a$} can be regarded as the \textit{classical} probability amplitudes associated with being in the $\ket{0}$ or $\ket{1}$ basis state, while $b$ characterises to what extent it is a classical mixture of these two states (for \mbox{$b=0$}) or a coherent superposition of them (for \mbox{$|b|=a(1-a)$}).

>>>>

Therefore, referring back to the qubit example in Eq.~(\ref{eq:2x2density}), $a$ and \mbox{$1-a$} can be regarded as the \textit{classical} probability amplitudes associated with being in the $\ket{0}$ or $\ket{1}$ basis state, while $b$ characterises to what extent it is a classical mixture of these two states (for \mbox{$b=0$}) or a coherent superposition of them (for \mbox{$|b|=\sqrt{a(1-a)}$}).

### 2018-12-29 Sections/intro_to_QO.tex
Photos update

A particularly ubiquitous state that emerges in CV representations is the \textit{coherent state}\index{Coherent states}, which closely approximates classical laser light\index{Laser},
\begin{align}\index{Coherent states}
\ket{\alpha} = e^{-\frac{|\alpha|^2}{2}} \sum_{n=0}^\infty \frac{\alpha^n}{\sqrt{n!}} \ket{n},
\end{align}
where \mbox{$\alpha\in\mathbb{C}$} is the complex coherent amplitude. Alternately, coherent states can be defined as the eigenstates of the annihilation operator,
\begin{align}
\hat{a}\ket{\alpha} = \alpha\ket{\alpha}.
\end{align}
Writing the coherent amplitude as,
\begin{align}
	\alpha=re^{i\theta},
\end{align}
$r$ can be interpreted as the strength of the classical field, and $\theta$ as its local phase.

>>>>

A particularly ubiquitous state that emerges in CV representations is the \textit{coherent state}\index{Coherent states}, which closely approximates classical laser light\index{Lasers},
\begin{align}\index{Coherent states}
\ket{\alpha} = e^{-\frac{|\alpha|^2}{2}} \sum_{n=0}^\infty \frac{\alpha^n}{\sqrt{n!}} \ket{n},
\end{align}
where \mbox{$\alpha\in\mathbb{C}$} is the complex coherent amplitude. Alternately, coherent states can be defined as the eigenstates of the annihilation operator,
\begin{align}
\hat{a}\ket{\alpha} = \alpha\ket{\alpha}.
\end{align}
Writing the coherent amplitude as,
\begin{align}
	\alpha=re^{i\theta},
\end{align}
$r$ can be interpreted as the strength of the classical field, and $\theta$ as its local phase.

### 2018-12-29 Sections/mathematical_representation_of_quantum_networks.tex
Restructured microwaves
Finito first round of indexing
Photos update

We consider a classical network to be a weighted, directed graph,
\begin{align}\index{Network!Graphs}
	G=(V,E),
\end{align}
where vertices represent \textit{nodes} (\mbox{$v\in V$}) in the network, and the weighted edges represent communication \textit{links} (\mbox{$e\in E$}) between neighbouring nodes \cite{???}.

@@

\begin{definition}[Network cost metrics] \label{def:metric} Cost metrics satisfy the properties:\index{Network!Cost metrics}
	\begin{itemize}
    	\item Identity operations: If a channel performs nothing, its associated cost is zero, \mbox{$c(\mathbb{\hat{I}}) = 0$}.
    	\item Triangle inequality: \\ $c(v_1\to v_2\to v_3) \leq c(v_1\to v_2) + c(v_2\to v_3)$, \\ across all paths \mbox{$v_1 \to v_2 \to v_3$}. In the case of strict equality under addition we refer to the cost as a \textit{strictly additive cost}.
    	\item Positivity: \mbox{$c\geq 0$}. This ensures that shortest-path algorithms will function correctly. It is also congruent with the intuitive expectation that data traversing a communications channel is not somehow better off than if it hadn't traversed that channel at all.
	\end{itemize}
\end{definition}
Attributes, on the other hand do not have a distance interpretation, and may have arbitrary structure. A detailed discussion on the relationship between costs and attributes is presented in Sec.~\ref{sec:c_vs_a}.

@@

\subsection{Strategy optimisation} \label{sec:strat_opt} \index{Strategy optimisation}

>>>>

We consider a classical network to be a weighted, directed graph,
\begin{align}\index{Network!Graphs}\index{Graphs}
	G=(V,E),
\end{align}
where vertices represent \textit{nodes} (\mbox{$v\in V$}) in the network, and the weighted edges represent communication \textit{links} (\mbox{$e\in E$}) between neighbouring nodes \cite{???}.

@@

\begin{definition}[Network cost metrics] \label{def:metric} Cost metrics satisfy the properties:\index{Network!Cost metrics}
	\begin{itemize}
    	\item Identity operations: If a channel performs nothing, its associated cost is zero, \mbox{$c(\hat\openone) = 0$}.
    	\item Triangle inequality: \\ $c(v_1\to v_2\to v_3) \leq c(v_1\to v_2) + c(v_2\to v_3)$, \\ across all paths \mbox{$v_1 \to v_2 \to v_3$}. In the case of strict equality under addition we refer to the cost as a \textit{strictly additive cost}.
    	\item Positivity: \mbox{$c\geq 0$}. This ensures that shortest-path algorithms will function correctly. It is also congruent with the intuitive expectation that data traversing a communications channel is not somehow better off than if it hadn't traversed that channel at all.
	\end{itemize}
\end{definition}
Attributes, on the other hand do not have a distance interpretation, and may have arbitrary structure. A detailed discussion on the relationship between costs and attributes is presented in Sec.~\ref{sec:c_vs_a}.

@@

\subsection{Strategy optimisation} \label{sec:strat_opt} \index{Strategy!Optimisation}

### 2018-12-29 Sections/optical_encoding_of_quantum_information.tex
Photos update

In some quantum protocols, although the inner workings may be quantum mechanical in nature, the inputs and outputs needn't capture any quantum coherence -- sometimes \textit{classical} information is sufficient for communications. As discussed above, coherent states are the archetypal example of this, and this is in fact the norm in present-day classical fibre-optic communication, where coherent states prepared via laser diodes\index{Laser!Diodes} are employed.

>>>>

In some quantum protocols, although the inner workings may be quantum mechanical in nature, the inputs and outputs needn't capture any quantum coherence -- sometimes \textit{classical} information is sufficient for communications. As discussed above, coherent states are the archetypal example of this, and this is in fact the norm in present-day classical fibre-optic communication, where coherent states prepared via laser diodes\index{Lasers!Diodes} are employed.

### 2018-12-29 Sections/physical_architectures_for_quantum_computing.tex
Photos update

The first key observation then is that gate teleportation can be used to shift this non-determinism to a resource state preparation stage, as described in detail in Sec.~\ref{sec:teleport_gate}. However, this is not the end of the story, since gate teleportation requires Bell state projections, which are themselves non-deterministic using purely linear optics (either using PBSs or CNOT gates). \latinquote{Ignotum per ignotius}.

@@

\paragraph{The \textsc{BosonSampling} model} \index{Boson-sampling}

@@

To see how matrix permanents naturally arise in this setting, it is easiest to explain by example. In Fig.~\ref{fig:BS_2_comb} we illustrate a simple interferometer, fed with two photons. We wish to calculate the output amplitude of measuring a photon in each of the modes 2 and 3, given photons input at modes 1 and 2. To evaluate this amplitude we simply need to add up the amplitudes of all possible paths yielding the desired outcome. In this simple example this sum-of-paths\index{Sum-of-paths} is given by,
\begin{align} \label{eq:BS_2_ph_comb}
\gamma_{\{2,3\}} &= \underbrace{U_{1,2}U_{2,3}}_{\mathrm{don't\ swap}} + \underbrace{U_{1,3}U_{2,2}}_{\mathrm{swap}} \nonumber \\
&= \mathrm{Per} \left[ {\begin{array}{cc}
   U_{1,2} & U_{2,2} \\
   U_{1,3} & U_{2,3} \\
  \end{array} } \right],
\end{align}
from which it is immediately clear that the amplitude is given by the sum of \mbox{$2!=2$} paths\footnote{The number of paths scales as $n!$ in general, which corresponds to the $n!$ order of the symmetric group, $S_n$, in the definition of the permanent from Eq.~(\ref{eq:permanent}).}, the permanent of the \mbox{$2\times 2$} matrix obtained from taking the columns (rows) of $\hat{U}$ where a photon is present at the respective input (output) mode.

@@

In Fig.~\ref{fig:BS_3_comb} we present to next most sophisticated example of an interferometer fed by 3 photons, for which the sum-of-paths\index{Sum-of-paths} has \mbox{$3!=6$} terms, given by,
\begin{align} \label{eq:BS_3_ph_comb}
\gamma_{\{1,2,3\}} &= U_{1,1}U_{2,2}U_{3,3} + U_{1,1}U_{3,2}U_{2,3} \nonumber \\
&+ U_{2,1}U_{1,2}U_{3,3} + U_{2,1}U_{3,2}U_{1,3} \nonumber \\
&+ U_{3,1}U_{1,2}U_{2,3} + U_{3,1}U_{2,2}U_{1,3}
\nonumber \\
&= \mathrm{Per} \left[ {\begin{array}{ccc}
   U_{1,1} & U_{2,1} & U_{3,1} \\
   U_{1,2} & U_{2,2} & U_{3,2} \\
   U_{1,3} & U_{2,3} & U_{3,3} \\
  \end{array} } \right],
\end{align}
and it is now clear upon inspection that the amplitude is given by a \mbox{$3\times 3$} matrix permanent.

@@

\paragraph{Problem description}

@@

\paragraph{Multiplexed \textsc{BosonSampling}} \index{Multiplexed!Boson-sampling}

@@

\paragraph{Scattershot \textsc{BosonSampling}} \index{Scattershot boson-sampling}

@@

A phase-shifter\index{Phase!Shifts}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat{n}},
\end{align}
where \mbox{$\hat{n}=\hat a^\dag \hat a$} is the photon-number operator\index{Photon-number operator}, rotates a state in phase-space by angle $\theta$ about the origin, implementing the transformation between the position and momentum operators,
\begin{align}\label{eq:xp_theta}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}
\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in position/momentum space.

@@

Qubits may be engineered by considering the lowest two energy levels of a quantum system. Based on the spacing between their energy levels, such quantum systems are classified into two categories:
\begin{itemize}
	\item Quantum harmonic oscillator type: have equal spacing between energy levels.\index{Quantum harmonic oscillators}
	\item Atomic type: have unequal spacing between energy levels.\index{Artificial atoms}
\end{itemize}
We illustrate these two cases in Fig.~\ref{fig:artificial_atom_energy_levels}, with their corresponding energy level diagrams. The energy levels of these two classes of systems obey,
\begin{align}
E_{n} &= \hbar \omega \left(n+\frac{1}{2}\right) \quad (\mathrm{Oscillator\,levels}), \nonumber \\ 
E_{n} &= -\frac{E_{0}}{n^{2}} \quad (\mathrm{Atomic\,levels}),
\end{align}
where \mbox{$n\in\mathbb{Z}^+$} denotes the discrete energy level, $\omega$ is optical frequency, and $E_0$ is the lowest-lying ground state energy\index{Ground states}.

>>>>

The first key observation then is that gate teleportation can be used to shift this non-determinism to a resource state preparation stage, as described in detail in Sec.~\ref{sec:teleport_gate}. However, this is not the end of the story, since gate teleportation requires Bell state projections, which are themselves non-deterministic using purely linear optics (either using PBSs or CNOT gates).

\latinquote{Ignotum per ignotius}.

@@

\paragraph{The \textsc{BosonSampling} model} \index{Boson-sampling!Model}

@@

To see how matrix permanents naturally arise in this setting, it is easiest to explain by example. In Fig.~\ref{fig:BS_2_comb} we illustrate a simple interferometer, fed with two photons. We wish to calculate the output amplitude of measuring a photon in each of the modes 2 and 3, given photons input at modes 1 and 2. To evaluate this amplitude we simply need to add up the amplitudes of all possible paths yielding the desired outcome. In this simple example this sum-of-paths\index{Sum-of-paths} is given by,
\begin{align} \label{eq:BS_2_ph_comb}
\gamma_{\{2,3\}} &= \underbrace{U_{1,2}U_{2,3}}_{\mathrm{don't\ swap}} + \underbrace{U_{1,3}U_{2,2}}_{\mathrm{swap}} \nonumber \\
&= \mathrm{Per}\begin{pmatrix}
   U_{1,2} & U_{2,2} \\
   U_{1,3} & U_{2,3}
  \end{pmatrix},
\end{align}
from which it is immediately clear that the amplitude is given by the sum of \mbox{$2!=2$} paths\footnote{The number of paths scales as $n!$ in general, which corresponds to the $n!$ order of the symmetric group, $S_n$, in the definition of the permanent from Eq.~(\ref{eq:permanent}).}, the permanent of the \mbox{$2\times 2$} matrix obtained from taking the columns (rows) of $\hat{U}$ where a photon is present at the respective input (output) mode.

@@

In Fig.~\ref{fig:BS_3_comb} we present to next most sophisticated example of an interferometer fed by 3 photons, for which the sum-of-paths\index{Sum-of-paths} has \mbox{$3!=6$} terms, given by,
\begin{align} \label{eq:BS_3_ph_comb}
\gamma_{\{1,2,3\}} &= U_{1,1}U_{2,2}U_{3,3} + U_{1,1}U_{3,2}U_{2,3} \nonumber \\
&+ U_{2,1}U_{1,2}U_{3,3} + U_{2,1}U_{3,2}U_{1,3} \nonumber \\
&+ U_{3,1}U_{1,2}U_{2,3} + U_{3,1}U_{2,2}U_{1,3}
\nonumber \\
&= \mathrm{Per} \begin{pmatrix}
   U_{1,1} & U_{2,1} & U_{3,1} \\
   U_{1,2} & U_{2,2} & U_{3,2} \\
   U_{1,3} & U_{2,3} & U_{3,3}
  \end{pmatrix},
\end{align}
and it is now clear upon inspection that the amplitude is given by a \mbox{$3\times 3$} matrix permanent.

@@

\paragraph{Problem description}\index{Boson-sampling!Problem description}

@@

\paragraph{Multiplexed \textsc{BosonSampling}} \index{Boson-sampling!Multiplexed}

@@

\paragraph{Scattershot \textsc{BosonSampling}} \index{Boson-sampling!Scattershot}

@@

A phase-shifter\index{Phase!Shifts}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat{n}},
\end{align}
where $\hat{n}$ is the photon-number operator\index{Photon-number!Operators}, rotates a state in phase-space by angle $\theta$ about the origin, implementing the transformation between the position and momentum operators,
\begin{align}\label{eq:xp_theta}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}
\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in position/momentum space.

@@

Qubits may be engineered by considering the lowest two energy levels of a quantum system. Based on the spacing between their energy levels, such quantum systems are classified into two categories:
\begin{itemize}
	\item Quantum harmonic oscillator type\index{Quantum harmonic oscillators}: have equal spacing between energy levels, given by,
	\begin{align}
	E_{n} &= \hbar \omega \left(n+\frac{1}{2}\right),
	\end{align}
	where \mbox{$n\in\mathbb{Z}^+$} denotes the discrete energy level, $\omega$ is optical frequency, and $E_0$ is the lowest-lying ground state energy\index{Ground states}.
	\item Atomic type\index{Artificial atoms}: have unequal spacing between energy levels, given by,
	\begin{align}
	E_{n} &= -\frac{E_{0}}{n^{2}}.
	\end{align}
\end{itemize}
We illustrate these two cases in Fig.~\ref{fig:artificial_atom_energy_levels}, with their corresponding energy level diagrams.

### 2018-12-29 Sections/protocols_for_the_quantum_internet.tex
Photos update

Mathematically, the measurement operators for number-resolved detection are,
\begin{align}\index{Number-resolved photo-detectors}
\hat\Pi_n = \eta^{n} \sum_{m=n}^\infty \binom{m}{n} (1-\eta)^{m-n} \ket{m}\bra{m},
\end{align}
for measurement outcome $n$, in the photon-number basis. And for non-number-resolved detection,
\begin{align}\index{Non-number-resolved photo-detectors}
&\hat\Pi_0 = \sum_{m=0}^\infty (1-\eta)^{m} \ket{m}\bra{m}, \nonumber \\
&\hat\Pi_{>0} = \mathbb{\hat{I}} - \hat\Pi_0.
\end{align}
Thus, inefficiency results in projection onto the wrong photon-number, making measurement outcomes incorrect.

@@

Furthermore, photo-detectors are subject to `dead-time'\index{Dead-time}, which renders them inactive for a finite recovery period following a detection event. This is of especial importance in time-bin-encoded schemes (Sec.~\ref{sec:time_bin}), where detectors must resolve photons over very short timescales on the order of nanoseconds. Dead-time can be modelled as a time-dependent efficiency of the form,
\begin{align}
\eta(t) = \left\{\begin{array}{cc}
 0, & t<\tau_\mathrm{dt} \\
 \eta_\mathrm{ss}, & t\geq\tau_\mathrm{dt} \\
\end{array}\right.,
\end{align}
where $t$ is time, $\tau_\mathrm{dt}$ is the detector's dead time\index{Dead time}, and $\eta_\mathrm{ss}$ is the detector's steady-state efficiency (i.e when not dead).

>>>>

Mathematically, the measurement operators for inefficient number-resolved detection are,
\begin{align}\index{Number-resolved photo-detectors}
\hat\Pi_n = \eta^{n} \sum_{m=n}^\infty \binom{m}{n} (1-\eta)^{m-n} \ket{m}\bra{m},
\end{align}
for measurement outcome $n$, in the photon-number basis. And for non-number-resolved detection,
\begin{align}\index{Non-number-resolved photo-detectors}
&\hat\Pi_0 = \sum_{m=0}^\infty (1-\eta)^{m} \ket{m}\bra{m}, \nonumber \\
&\hat\Pi_{>0} = \hat\openone - \hat\Pi_0.
\end{align}
Thus, inefficiency results in projection onto the wrong photon-number, making measurement outcomes incorrect.

@@

Furthermore, photo-detectors are subject to `dead-time'\index{Dead-time}, which renders them inactive for a finite recovery period following a detection event. This is of especial importance in time-bin-encoded schemes (Sec.~\ref{sec:time_bin}), where detectors must resolve photons over very short timescales on the order of nanoseconds. Dead-time can be modelled as a time-dependent efficiency of the form,
\begin{align}
\eta(t) = \left\{\begin{array}{l l}
 0, & t<\tau_\mathrm{dt} \\
 \eta_\mathrm{ss}, & t\geq\tau_\mathrm{dt} \\
\end{array}\right.,
\end{align}
where $t$ is time, $\tau_\mathrm{dt}$ is the detector's dead time\index{Dead time}, and $\eta_\mathrm{ss}$ is the detector's steady-state efficiency (i.e when not dead).

### 2018-12-29 Sections/quantum_channels.tex
Circuit for shor
Improved QM intro
Formatting update
Photos update

Quantum processes are most easily represented using \textit{Kraus operators}\index{Kraus operators}, $\{\hat{K}_i\}$,
\begin{align} \label{eq:kraus_rep}
\mathcal{E}(\hat\rho) = \sum_i \hat{K}_i \hat\rho \hat{K}_i^\dag,
\end{align}
where,
\begin{align}
\sum_i \hat{K}_i^\dag \hat{K}_i = \hat{\mathbb{I}},
\end{align}
for normalisation. Here $\mathcal{E}$ is a super-operator, denoting the action of the process on state $\hat\rho$. This is also referred to as the \textit{operator-sum representation}\index{Kraus operators}. This representation has the elegant interpretation as the probabilistic application of each of the Kraus operators $\hat{K}_i$, with probability,
\begin{align}
p_i = \mathrm{tr}(\hat{K}_i \hat\rho \hat{K}_i^\dag).
\end{align}
In the ideal case, the two types of evolution of interest are unitary evolution, in which case there is only one Kraus operator, \mbox{$\hat{K}_1=\hat{U}$}, and projective measurement, where there is again only one Kraus operator, \mbox{$\hat{K}_1=\ket{m}\bra{m}$}, for measurement outcome $m$.

@@

\begin{figure}[!htbp]
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\hat\rho_S} & \multigate{1}{\hat{U}_{S,E}} & \qw & \,\,\,\,\,\mathcal{E}(\hat\rho_S) \\
    \lstick{\ket{0}_E} & \ghost{\hat{U}_{S,E}} & \qw & \times \\
} \nonumber
\end{align}
\captionspacefig \caption{Model for the quantum process formalism, as a system state $\hat\rho_S$ undergoing joint unitary evolution with an environment state $\ket{0}_E$, which is subsequently traced out, yielding an arbitrary quantum process $\mathcal{E}(\hat\rho_S)$ acting on the primary system. For the most general possible class of quantum processes to be enabled, the dimension of the environment Hilbert space must grows quadratically with the dimension of the primary Hilbert space.\index{Hilbert space}} \label{fig:q_proc}
\end{figure}

@@

For example, for a single qubit, the Pauli operators\index{Pauli!Operators} -- $\hat\sigma_1$ (identity, $\mathbb{\hat{I}}$), $\hat\sigma_2$ (bit-flip, $\hat{X}$), $\hat\sigma_3$ (bit-phase-flip, $\hat{Y}$), and $\hat\sigma_4$ (phase-flip, $\hat{Z}$) -- are complete for single-qubit operations ($\mathbb{C}_2$). Therefore by decomposing our Kraus operators into linear combinations of these basis operators we have a standardised representation for single-qubit processes. Formally, for one qubit,
\begin{align} \label{eq:process_matrix}
\mathcal{E}(\hat\rho) = \sum_{i,j=1}^4 \chi_{i,j} \hat{\sigma}_i\hat\rho\,\hat{\sigma}_j^\dag.
\end{align}

@@

Process matrices share many algebraic properties and interpretations in common with density matrices. The diagonal elements can be regarded as the amplitudes associated with applying each of the four Pauli operators, all of which are non-negative, while the off-diagonal elements represent the coherences between them, i.e whether the operations on the diagonal are being applied probabilistically or coherently. For example, a process that simply randomly applies Pauli operators would have a diagonal process matrix in the Pauli basis. But off-diagonal elements would be indicative of applying coherent superpositions of the operators.

@@

As an illustrative example of the interpretation of process matrices, in Fig.~\ref{fig:CNOT_proc_matrix} we show the process matrix for the CNOT gate, represented in the Pauli basis. The CNOT operator can be expressed in the Pauli operator basis as,
\begin{align}
\hat{U}_\mathrm{CNOT} = \frac{1}{2}(\hat{\mathbb{I}}\otimes \hat{\mathbb{I}} + \hat{\mathbb{I}} \otimes \hat{X} + \hat{Z}\otimes \hat{\mathbb{I}} - \hat{Z}\otimes \hat{X}).
\end{align}
Then, some density operator evolved under the CNOT gate is simply \mbox{$\hat{U}_\mathrm{CNOT}\hat\rho \,\hat{U}_\mathrm{CNOT}^\dag$}. Expanding this out, we obtain a new state comprising 16 terms, each representing the action of some combination of Pauli operators from the left and from the right. The amplitudes of these terms exactly correspond to the 16 non-zero elements of the process matrix shown in Fig.~\ref{fig:CNOT_proc_matrix}.

@@

The first stage in QPT is \textit{quantum state tomography} (QST), where the goal is to reconstruct and unknown density matrix via measurements upon multiple copies of the state. QST is based upon the simple observation that the completeness relation\index{Completeness relation} for an arbitrary state can be expressed,
\begin{align}
\hat\rho = \sum_i \mathrm{tr}(\hat{E}_i\hat\rho)\cdot\hat{E}_i,
\end{align}
where $\{\hat{E}_i\}$ forms a complete basis for the Hilbert space of $\hat\rho$. For a single qubit this decomposition is most often performed in the Pauli basis, 
\begin{align}
\hat\rho = \mathrm{tr}(\hat\rho)\cdot\hat{\mathbb{I}} + \mathrm{tr}(\hat{X}\hat\rho)\cdot\hat{X} + \mathrm{tr}(\hat{Y}\hat\rho)\cdot\hat{Y} +\mathrm{tr}(\hat{Z}\hat\rho)\cdot\hat{Z}.
\end{align}
Of course, \mbox{$\mathrm{tr}(\hat{E}\hat\rho) = P(\hat{E}|\hat\rho)$} is just the expectation value of the measurement operator $\hat{E}$ when measuring $\hat\rho$. Thus, measuring the expectation values in each of the four Pauli bases reconstructs $\hat\rho$.

>>>>

Quantum processes are most easily represented using \textit{Kraus operators}\index{Kraus operators}, $\{\hat{K}_i\}$,
\begin{align} \label{eq:kraus_rep}
\mathcal{E}(\hat\rho) = \sum_i \hat{K}_i \hat\rho \hat{K}_i^\dag,
\end{align}
where,
\begin{align}
\sum_i \hat{K}_i^\dag \hat{K}_i = \hat\openone,
\end{align}
for normalisation. Here $\mathcal{E}$ is a super-operator, denoting the action of the process on state $\hat\rho$. This is also referred to as the \textit{operator-sum representation}\index{Kraus operators}. This representation has the elegant interpretation as the probabilistic application of each of the Kraus operators $\hat{K}_i$, with probability,
\begin{align}
p_i = \mathrm{tr}(\hat{K}_i \hat\rho \hat{K}_i^\dag).
\end{align}
In the ideal case, the two types of evolution of interest are unitary evolution, in which case there is only one Kraus operator, \mbox{$\hat{K}_1=\hat{U}$}, and projective measurement, where there is again only one Kraus operator, \mbox{$\hat{K}_1=\ket{m}\bra{m}$}, for measurement outcome $m$.

@@

\begin{figure}[!htbp]
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\hat\rho_S} & \multigate{1}{{U}_{S,E}} & \qw & \,\,\,\,\,\mathcal{E}(\hat\rho_S) \\
    \lstick{\ket{0}_E} & \ghost{\hat{U}_{S,E}} & \qw & \times \\
} \nonumber
\end{align}
\captionspacefig \caption{Model for the quantum process formalism, as a system state $\hat\rho_S$ undergoing joint unitary evolution with an environment state $\ket{0}_E$, which is subsequently traced out, yielding an arbitrary quantum process $\mathcal{E}(\hat\rho_S)$ acting on the primary system. For the most general possible class of quantum processes to be enabled, the dimension of the environment Hilbert space must grows quadratically with the dimension of the primary Hilbert space.\index{Hilbert space}} \label{fig:q_proc}
\end{figure}

@@

For example, for a single qubit, the Pauli operators\index{Pauli!Operators} -- $\hat\sigma_1$ (identity, $\hat\openone$), $\hat\sigma_2$ (bit-flip, $\hat{X}$), $\hat\sigma_3$ (bit-phase-flip, $\hat{Y}$), and $\hat\sigma_4$ (phase-flip, $\hat{Z}$) -- are complete for single-qubit operations ($\mathbb{C}_2$). Therefore by decomposing our Kraus operators into linear combinations of these basis operators we have a standardised representation for single-qubit processes. Formally, for one qubit,
\begin{align} \label{eq:process_matrix}
\mathcal{E}(\hat\rho) = \sum_{i,j=1}^4 \chi_{i,j} \hat{\sigma}_i\hat\rho\,\hat{\sigma}_j^\dag.
\end{align}

@@

Process matrices share many algebraic properties and interpretations in common with density matrices. The diagonal elements can be regarded as the amplitudes associated with applying each of the four Pauli operators, all of which are non-negative, while the off-diagonal elements represent the coherences between them, i.e whether the operations on the diagonal are being applied probabilistically or coherently. For example, a process that simply randomly applies Pauli operators would have a diagonal process matrix in the Pauli basis. But off-diagonal elements would be indicative of applying coherent superpositions of the operators. Like density matrices, the dimensionality of process matrices grows exponentially with the number of qubits in the system being characterised, and for exactly the same conceptual reasons.

@@

As an illustrative example of the interpretation of process matrices, in Fig.~\ref{fig:CNOT_proc_matrix} we show the process matrix for the CNOT gate, represented in the Pauli basis. The CNOT operator can be expressed in the Pauli operator basis as,
\begin{align}
\hat{U}_\mathrm{CNOT} = \frac{1}{2}(\hat\openone\otimes \hat\openone + \hat\openone \otimes \hat{X} + \hat{Z}\otimes \hat\openone - \hat{Z}\otimes \hat{X}).
\end{align}
Then, some density operator evolved under the CNOT gate is simply \mbox{$\hat{U}_\mathrm{CNOT}\hat\rho \,\hat{U}_\mathrm{CNOT}^\dag$}. Expanding this out, we obtain a new state comprising 16 terms, each representing the action of some combination of Pauli operators from the left and from the right. The amplitudes of these terms exactly correspond to the 16 non-zero elements of the process matrix shown in Fig.~\ref{fig:CNOT_proc_matrix}.

@@

The first stage in QPT is \textit{quantum state tomography} (QST), where the goal is to reconstruct and unknown density matrix via measurements upon multiple copies of the state. QST is based upon the simple observation that the completeness relation\index{Completeness relation} for an arbitrary state can be expressed,
\begin{align}
\hat\rho = \sum_i \mathrm{tr}(\hat{E}_i\hat\rho)\cdot\hat{E}_i,
\end{align}
where $\{\hat{E}_i\}$ forms a complete basis for the Hilbert space of $\hat\rho$. For a single qubit this decomposition is most often performed in the Pauli basis, 
\begin{align}
\hat\rho = \mathrm{tr}(\hat\rho)\cdot\hat\openone + \mathrm{tr}(\hat{X}\hat\rho)\cdot\hat{X} + \mathrm{tr}(\hat{Y}\hat\rho)\cdot\hat{Y} +\mathrm{tr}(\hat{Z}\hat\rho)\cdot\hat{Z}.
\end{align}
Of course, \mbox{$\mathrm{tr}(\hat{E}\hat\rho) = P(\hat{E}|\hat\rho)$} is just the expectation value of the measurement operator $\hat{E}$ when measuring $\hat\rho$. Thus, measuring the expectation values in each of the four Pauli bases reconstructs $\hat\rho$.
